Responses to the reviews of ACL rolling review paper \#162: ``Latent Group Dropout for Multilingual and Multidomain Machine Translation''

### 2022-01-13 2022/acl/responses.tex
merge remote changes from FY
answers for todos in responses.text

For the sake of the clarification of our approach, we would like to point out several misunderstandings in the summary made by Reviewer iMf4:
\begin{itemize}
\item Our approach does not aim to find task-specific and task-agnostic \textbf{parameters} in the neural network: there is no notion of domain-specific or domain-agnostic parameters in the approach we present. The objective of our algorithm is to optimize the assignment \emph{of a sub-group of "nodes"}, at the output of each intermediate layer, to each task.
\item Our approach does not mask the sub-parts of each weight matrix, but instead it masks a fixed number of sub-groups of elements of the output of each intermediate layer.
\end{itemize}
We have tried to improve our presentation of our method in the revised version of the paper to avoid further misunderstandings.\todo{Change presention, give line numbers}

We would like to answer the other concerns of the reviewier as follows. \todo{CLAIM : baseline + parameter sharing + resultats CDR}
\begin{itemize} 
\item Regarding baselines, we generally refer to the rebuttal to the meta review. Note that according to your suggestion, we have added new multidomain experiments with a heuristic definition of blocks. See the updated table~XXX.\Todo{Add table}
\item We have now included an analysis on the effect of $k$ on the performance in the revised version (see new section 4.4)
\item The multilingual experiments use two groups of $8$ languages, which are all low-resourced; this might lower the significance of the improvement as observed in the paper of Lin et al. 21 (only +0.7 for low resource languages). Our method significantly improves the less resources languages among these groups.
\item As suggested, we are now using heatmaps instead of Table 7.
\item Statistical confidence scores are also reported. \todo{Add significancy tests}
\end{itemize}
}

@@

\begin{itemize}
\item We initialize the probabilistic distribution of the latent variables as uniform distribution. This is clarified in the revised text.\Todo{Check clarified which line}
\item The revised version includes a discussion  regarding $k$ and how it affects the performance of our approach (section 4.4).
\item As reported in many works using the Gumbel reparameterization trick, the effect of $\tau$ is relatively insignificant. This is discussed in the revised version in section XXXX. \Todo{which section}Therefore, we focused more on selecting $k$. \Todo{Add references}
\item Because we would like to have the same \emph{total amount of training iterations between Adapter-based and LaMGD}, we extend the training of LaMGD to 300K. The convergence of the standard Transformer is achieved before 200K as its validation curve became flat near the 200K-th iteration. These has been clarified in the paper. \Todo{Which section ?}
\item The same answer applies to the reviewer's concern regarding the multilingual experiments.
\item As pointed out\todo{Where ?}, significant gains are observed in several very low-resourced languages, not globally. This might be explained by the fact that low-resourced languages benefit most from the sharing nodes with a related well-resourced languages, and are also less affected by the inference of unrelated languages.
\end{itemize}

Our claim on the advantage in computational cost wrt. Adapters relies on the inference stage while there are no extra parameters added to the standard Transformer compared to Adapter-based methods. At the same time, the training time will  more than usual because of the joint optimization of the network's organization and the parameters. \todo{Not so great. Can we say more ? There is a nice blog post on FLOPS here: \url{%
https://medium.com/@dzmitrybahdanau/the-flops-calculus-of-language-model-training-3b19c1f025e4
}%
}
}%

>>>>

For the sake of the clarification of our approach, we would like to point out several misunderstandings in the summary made by Reviewer iMf4:
\begin{itemize}
\item Our approach does not aim to find task-specific and task-agnostic \textbf{parameters} in the neural network: there is no notion of domain-specific or domain-agnostic parameters in the approach we present. The objective of our algorithm is to optimize the assignment \emph{of a sub-group of "nodes"}, at the output of each intermediate layer, to each task.
\item Our approach does not mask the sub-parts of each weight matrix, but instead it masks a fixed number of sub-groups of elements of the output of each intermediate layer.
\end{itemize}
We have tried to improve our presentation of our method in the revised version of the paper to avoid further misunderstandings.\todo{Change presentation, give line numbers}

We would like to answer the other concerns of the reviewier as follows. \todo{CLAIM : baseline + parameter sharing + resultats CDR}
\begin{itemize} 
\item Regarding baselines, we generally refer to the rebuttal to the meta review. Note that according to your suggestion, we have added new multidomain experiments with a heuristic definition of blocks. See the updated table $3$.\Todo{Add table}
\item We have now included an analysis on the effect of $k$ on the performance in the revised version (see new section 4.4)
\item The multilingual experiments use two groups of $8$ languages, which are all low-resourced; this might lower the significance of the improvement as observed in the paper of Lin et al. 21 (only +0.7 for low resource languages). Our method significantly improves the less resources languages among these groups.
\item As suggested, we are now using heatmaps instead of Table 7.
\item Statistical confidence scores are also reported. \todo{Add significancy tests}
\end{itemize}
}

@@

\begin{itemize}
\item We initialize the probabilistic distribution of the latent variables as uniform distribution. This is clarified in the revised text in Section$3.1.4$.\Todo{Check clarified which line}
\item The revised version includes a discussion regarding $k$ and how it affects the performance of our approach (section 4.4).
\item As reported in many works using the Gumbel reparameterization trick, the effect of $\tau$ is relatively insignificant. This is discussed in the revised version in section $3.1.3$. \Todo{which section}Therefore, we focused more on selecting $k$. \Todo{Add references}
\item Because we would like to have the same \emph{total amount of training iterations between Adapter-based and LaMGD}, we extend the training of LaMGD to 300K. The convergence of the standard Transformer is achieved before 200K as its validation curve became flat near the 200K-th iteration. These has been clarified in the paper. \Todo{Which section ?} Section $3.1.1$
\item The same answer applies to the reviewer's concern regarding the multilingual experiments.
\item As pointed out\todo{Where ?} in Table 5, significant gains are observed in several very low-resourced languages, not globally. This might be explained by the fact that low-resourced languages benefit most from the sharing nodes with a related well-resourced languages, and are also less affected by the inference of unrelated languages.
\end{itemize}

Our claim on the advantage in computational cost wrt. Adapters relies on the inference stage while there are no extra parameters added to the standard Transformer compared to Adapter-based methods. At the same time, the training time will be more than usual because of the joint optimization of the network's organization and the parameters. \todo{Not so great. Can we say more ? There is a nice blog post on FLOPS here: \url{%
https://medium.com/@dzmitrybahdanau/the-flops-calculus-of-language-model-training-3b19c1f025e4
}%
}
}%
